Creating optimal conditions for reproducible data analysis in R with `fertile`

### 2020-03-15 fertile.Rmd
adding citations

Reproducibility is critically important to the advancement of knowledge in all fields of scientific research. Researchers are acknowledging this; publications focusing on reproducibility seem to have increased in frequency over the last several years [**CITATIONS HERE**]

@@

Broman reiterates the need for clear naming and file separation while sharing several additional suggestions: keep the project contained in one directory, use relative paths, and include a README. [**ADD CITATION FOR BROMAN**]

R OpenSci's [**EXPLAIN WHO THEY ARE**] reproducibility recommendations share similar principles to those discussed previously. They focus on a need for a well-developed file system, with no extraneous files and clear labeling. They also reiterate the need to note dependencies and use automation when possible, while making clear a suggestion not present in the previously-discussed literature: the need to use seeds, which allow  for the saving and restoring of the random number generator state, when running code involving randomness.

@@

  - Separate folders for different file types.

  - No extraneous files.

  - Minimal clutter.

@@

  - Files are clearly named, preferably in a way where the order in which they should be run is clear.

  - A README is present.

  - Dependencies are noted.

>>>>

Reproducibility is critically important to the advancement of knowledge in
all fields of scientific research. Researchers are acknowledging this; 
publications and discussions focusing on reproducibility seem to have 
increased in frequency over the last several years (@sep-scientific-reproducibility), (@plos-biology), (@bioessays-gosselin)

@@

Broman reiterates the need for clear naming and file separation while sharing several additional suggestions: keep the project contained in one directory, use relative paths, and include a README (@broman).

The reproducibility recommendations from R OpenSci, a non-profit initiative founded in 2011 to make scientific data retrieval reproducible, share similar principles to those discussed previously. They focus on a need for a well-developed file system, with no extraneous files and clear labeling. They also reiterate the need to note dependencies and use automation when possible, while making clear a suggestion not present in the previously-discussed literature: the need to use seeds, which allow  for the saving and restoring of the random number generator state, when running code involving randomness @r-opensci.

@@

  - Separate folders for different file types.
  - No extraneous files.
  - Minimal clutter.

@@

  - Files are clearly named, preferably in a way where the order in which they should be run is clear.
  - A README is present.
  - Dependencies are noted.
